---
title: "FA542"
author: "Zongqi"
date: "4/20/2022"
output:
  pdf_document: default
  html_document: default
---
```{r message=FALSE, warning=FALSE}
library(gdata)
stock <- read.csv("~/Documents/Stevens_second_semester/FA542/Homework/Homework5/homework05.csv")
nrow(stock)
o_rt <- stock[2:720,2]
o_rt_1 <- stock[1:719,2]
ct1 <- o_rt - o_rt_1

t_rt <- stock[2:720,3]
t_rt_1 <- stock[1:719,3]
ct10 <- t_rt - t_rt_1
r <- cbind(ct1, ct10)
```


$(i):$ single time series autoregressive models
```{r}
#par(c(2,2))
#plot.ts(stock$DGS1, main="MSFT prices", ylab="Prices")
#plot.ts(stock$DGS10, main="MSFT prices", ylab="Prices")
cr <- NA
for (p in 0:10){ 
    tmp = arima(ct1, order=c(p,0,0))
    cr <- cbind(cr,BIC(tmp))            
}
cr
#AR(8)is the best 
md1 <- arima(ct1 , order = c(8, 0, 0))

cr2 <- NA
for (p in 0:10){ 
    tmp = arima(ct10, order=c(p,0,0))
    cr2 <- cbind(cr2,BIC(tmp))            
}
cr2
md2 <- arima(ct10 , order = c(8, 0, 0))

```


$(ii) ; (iii)$
```{r}
library(vars)
mdl = VAR(r, lag.max = 8 , ic = "AIC" , type = "const")
summary(mdl)
C = summary(mdl)$covres # covariance matrix of innovations
C
# Structural form
smdl = BQ(mdl)
summary(smdl)

```

$ (iv) $
```{r}
length(ct1)
length(ct10)
train <- ct1[1:699]
train2 <- ct10[1:699]
test1 <- ct1[700:719]
test2 <- ct10[700:719]
```

prediction for md1 & md2
```{r}
predicted1 <- predict(md1, n.ahead = 20)$pred
predicted2 <- predict(md2, n.ahead = 20)$pred
mse1 <- mean((predicted1 - test1)^2)
mse2 <- mean((predicted2 - test2)^2)
mse1
mse2
```
I calculate the mean squared error here to evaluated the result of prediction.


prediction for mdl
```{r}
library(vars)
predictedvar <- predict(mdl, n.ahead = 20)
predictedvar_ct1 <- predictedvar$fcst$ct1[,1]
predictedvar_ct10 <- predictedvar$fcst$ct10[,1]
mse1_v <- mean((predictedvar_ct1 - test1)^2)
mse2_v <- mean((predictedvar_ct10 - test2)^2)
mse1_v
mse2_v

```
By compare the mean squared of single single time series autoregressive models and vector autoregressive model, here we can see for both ct1 and ct10, the single time series autoregressive models is the better.








